FAoptions

### 2024-01-15 FAoptions.Rmd
commiting after a long time. oh god

---
title: "FAoptions"
output:
  word_document: null
  keep_md: yes
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych))
library(officer)
library(magrittr)

@@

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

@@

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1)))
```

# Two factor solution is slightly different for Nuclear, Solar and Coal.

## Nuclear

@@

fascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7))) %>%
  na.omit()
ecopolall <- fascales %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")%>%
    rename(
      "Limits on Wealth " = "WEALTHLIM",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Centralisation" = "DECISIONCEN",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Pro Localeconomy" = "ECONOMYLOCAL",
      "Environment over Development" = "ENVOVERDEV",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Anti Regulations" = "OWNERNOREG",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
      "Health risk(nuclear)" = "HEALTHNUCLEAR",
      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
      "Community pride(nuclear)" = "PRIDENUCLEAR",
      "National pride(nuclear)" = "NPRIDENUCLEAR",
      "National development(nuclear)" = "DEVNUCLEAR",
      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
      "Reliance on government(nuclear)" = "RELYNUCLEAR"
    )

@@

@@

@@

rename_map <- c(
  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "Pro Private ownership" = "All businesses and industries should be owned privately",
  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "Pro Public ownership" = "The government should own most large businesses and industries",
  "Pro Regulations" = " Regardless of ownership, the government should pass strong regulations and implement them",
  "Displacement risk(nuclear)" = "Nuclear energy is leading to displacement of people from their land",
  "Spoils Natural Beauty(nuclear)" = "Nuclear energy spoils the natural beauty of the landscape",
  "Pollution risk(nuclear)" = "Nuclear energy increases pollution of air/water/land",
  "Health risk(nuclear)" = "Nuclear energy poses a great risk to the health of people living around it",
  "Job opportunities(nuclear)" = "Nuclear energy will bring jobs to the local community",
  "Community pride(nuclear)" = "I would be proud if my community used nuclear energy",
  "National pride(nuclear)" = "Nuclear energy is a mark of pride for our nation",
  "National development(nuclear)" = "Nuclear energy pushes forward the country's development",
  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions",
  "Reliance on government(nuclear)" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
)

@@

fa_table(ecopolall2.fa, .4) %>%
  rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("2 factor solution") %>%
  autofit()

@@

```{r, echo = FALSE}
ecopolall2.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename(Pdevelop = MR1, Ndevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for 2 Factor Solution")
```

\newpage
## Solar

@@

sfascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Solar","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR", "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7))) %>%
  na.omit()

@@

>>>>

---
title: "FAoptions"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document: 
    toc: yes
    toc_depth: 2
    keep_tex: yes
  keep_md: yes
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych))
suppressPackageStartupMessages(library(lavaan))
library(officer)
library(magrittr)

@@

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEVNUCLEAR","DEVSOLAR", "DEVCOAL", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
mutate_at(vars(starts_with (c("K_I","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

@@

# no - reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                                                         . == "Somewhat disagree" ~ 2,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 4,
                                                                                                         . == "Strongly agree" ~ 5)))%>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7)))
```

#sort demo vars

codedmodule2$State <- as.factor(codedmodule2$State)
codedmodule2$gender <- as.factor(codedmodule2$gender)
codedmodule2$Urban <- as.factor(codedmodule2$urban_rural)

codedmodule2$caste <- as.factor(codedmodule2$caste)
codedmodule2$religion <- as.factor(codedmodule2$religion)
# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
codedmodule2$Uppercaste <- ifelse(codedmodule2$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
codedmodule2$Male <- ifelse(codedmodule2$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)

codedmodule21 <- codedmodule2 %>%
            dplyr::select(Risky_Nuclear, Risky_Solar, Risky_Coal, Uppercaste, Male, Hindu, Urban, age, State) %>%
            na.omit()

# lm on nuclear energy with all demovars

alldemos <- codedmodule21 %>%
            dplyr::select(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, age, State) %>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7)))
```

```{r, echo=FALSE}
fascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR","SYSTEMDEMO","SYSTEMRELIGION", "SYSTEMTECHNO","SYSTEMTOTAL", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7))) %>%
  na.omit()
```

```{r, echo=FALSE}
# Q6: Does the Kahan scale explain perception of risk from nuclear energy and other DVs ?

# we conducted fa on the kahan scale 
# CFA for Kahan scale. We shouldn't do FA here since this a well used scale with theoretical basis for factor distinctions and also previous studies using the same scale

library(lavaan)
library(semTools)
library(kableExtra)

fascales <- codedmodule2 %>%
  filter(
    rowSums(is.na(dplyr::select(., starts_with("K_")))) == 0 &  # This line ensures that rows with any NA in columns starting with         "K_" are   filtered out.
    !is.na(WEALTHLIM) & 
    !is.na(MECHANISATION) & 
    !is.na(DECISIONDECEN) & 
    !is.na(DECISIONCEN) & 
    !is.na(INDUSTRYLARGE) & 
    !is.na(INDUSTRYSMALL) & 
    !is.na(ECONOMYGLOBAL) & 
    !is.na(ECONOMYLOCAL) & 
    !is.na(ENVOVERDEV) & 
    !is.na(DEVOVERENV) & 
    !is.na(OWNERPVT) & 
    !is.na(OWNERNOREG) & 
    !is.na(OWNERPUB) & 
    !is.na(OWNERREG) & 
    !is.na(DISPLACENUCLEAR) & 
    !is.na(POLLUTENUCLEAR) & 
    !is.na(HEALTHNUCLEAR) & 
    !is.na(JOBSNUCLEAR) & 
    !is.na(BEAUTYNUCLEAR) & 
    !is.na(PRIDENUCLEAR) & 
    !is.na(NPRIDENUCLEAR) & 
    !is.na(DEVNUCLEAR) & 
    !is.na(PROSPERNUCLEAR) & 
    !is.na(RELYNUCLEAR)
  )

fascales2 <- codedmodule2 %>%dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%na.omit()

Kahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA
Kahan_cfa <- cfa(Kahan_fas, data = fascales, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
#summary(Kahan_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit
#pvalue should be greater than 0.05 p > 0.0.5

# after having removed a few variables that had very low loading, the model is now a good fit, we have two latent variables - Hierarchy- egalitarian and Communitarian. Again we see that individualistic variables just don't fit here.

# creating table of factor scores

Kahan_scores <- predict(Kahan_cfa, newdata = fascales)

Kahan_Kscores <- cbind(fascales, Kahan_scores)

## RMSEA is still pretty big.

# the psych code for FA on eco-pol scale for nuclear energy - all vars combined

@@

ecopolall <- fascales %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "RELYNUCLEAR","PROSPERNUCLEAR", "JOBSNUCLEAR")%>%
    rename(
      "Limits on Wealth" = "WEALTHLIM",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Centralisation" = "DECISIONCEN",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Anti Large Industries" = "INDUSTRYSMALL",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Pro Localeconomy" = "ECONOMYLOCAL",
      "Environment over Development" = "ENVOVERDEV",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership" = "OWNERPVT",
      "Anti Regulations" = "OWNERNOREG",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
      "Pollution risk(nuclear)" = "POLLUTENUCLEAR",
      "Health risk(nuclear)" = "HEALTHNUCLEAR",
      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
      "Community pride(nuclear)" = "PRIDENUCLEAR",
      "National pride(nuclear)" = "NPRIDENUCLEAR",
      "National development(nuclear)" = "DEVNUCLEAR",
      "Reliance on government(nuclear)" = "RELYNUCLEAR"
    )

@@

#print.psych(ecopolall2.fa, cut = 0.4, sort = TRUE)

ecopol_fas <- '
  Pdevelop =~ HEALTHNUCLEAR + BEAUTYNUCLEAR + DISPLACENUCLEAR + POLLUTENUCLEAR + INDUSTRYSMALL + OWNERREG + MECHANISATION
  Ndevelop =~ DEVNUCLEAR + PROSPERNUCLEAR + PRIDENUCLEAR + NPRIDENUCLEAR + JOBSNUCLEAR
'
ecopol_cfa <- cfa(ecopol_fas, data = fascales, std.lv = TRUE)
#summary(ecopol_cfa, fit.measure= TRUE, standardized = TRUE)

@@

\blandscape
# FA on Combined Scale (2 Factor Solution): People Centered Development and Nationalist Development 
## Nuclear Energy: EFA on Combined Scale (2 Factor Solution)

@@

flex <- function(data, title=NULL, col_widths=NULL) {
  tbl <- flextable(data) %>%
           #padding(padding = 1, part = "all") %>%
           #set_table_properties(layout = "autofit") %>%
           fontsize(size=10, part="all") %>%
           set_caption(title, 
                       autonum = officer::run_autonum(seq_id = "tab", 
                                                      pre_label = "Table ", 
                                                      post_label = "\n", 
                                                      bkm = "anytable"))

  # If col_widths is provided, set column widths
  if(!is.null(col_widths)) {
    for(col in names(col_widths)){
      tbl <- width(tbl, j = col, width = col_widths[[col]])
    }
  }

  return(tbl)
}

rename_map <- c(
  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "Pro Private ownership" = "All businesses and industries should be owned privately",
  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "Pro Public ownership" = "The government should own most large businesses and industries",
  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
  "Displacement risk(nuclear)" = "Nuclear energy is leading to displacement of people from their land",
  "Spoils Natural Beauty(nuclear)" = "Nuclear energy spoils the natural beauty of the landscape",
  "Pollution risk(nuclear)" = "Nuclear energy increases pollution of air/water/land",
  "Health risk(nuclear)" = "Nuclear energy poses a great risk to the health of people living around it",
  "Job opportunities(nuclear)" = "Nuclear energy will bring jobs to the local community",
  "Community pride(nuclear)" = "I would be proud if my community used nuclear energy",
  "National pride(nuclear)" = "Nuclear energy is a mark of pride for our nation",
  "National development(nuclear)" = "Nuclear energy pushes forward the country's development",
  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions",
  "Reliance on government(nuclear)" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
)

@@

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      code = names(rename_map)[match(item, rename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    dplyr::select(code, everything()) # reorder columns to bring code to the front
}

fa_table(ecopolall2.fa, .4) %>%
  rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("2 factor solution", col_widths = list(Items = 4.5, code = 1.5))

@@

\elandscape

```{r, echo = FALSE}
ecopolall2.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename(Pdevelop = MR1, Ndevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for Combined Scale (2 Factor Solution)")
```

## Nuclear - linear regression with 2 Factor solution

# Linear Model with 2 factor solution for  Risk perception from Nuclear Energy

ecopolall_scores <- psych::factor.scores(ecopolall, ecopolall2.fa)

# The factor scores will be stored in the scores element of the returned list
scores1 <- ecopolall_scores$scores

#binding factor scores to the dataset

fascale_scores <- cbind(Kahan_Kscores, scores1) %>%
  rename(Pdevelop = MR1)%>%
  rename(Ndevelop = MR2)

nuclear2fa <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = fascale_scores)

#m2_allscales <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban +State+ KahanS + KahanH + NPRIDENUCLEAR + PRIDENUCLEAR + DEVNUCLEAR + PROSPERNUCLEAR, data = fascale_scores)
# Print model summary
#summary(nuclear2fa)

```
```{r,echo = FALSE}
acceptance2 <- fascale_scores %>%
  mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
         Hyrdo = Ben_Hydro - Risky_Hydro,
         Wind = Ben_Wind - Risky_Wind,
         Solar = Ben_Solar - Risky_Solar,
         Coal = Ben_Coal - Risky_Coal,
         Gas = Ben_Gas - Risky_Gas,
         Oil = Ben_Oil - Risky_Oil)

nuclearacceptlm <- lm(Nuclear ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = acceptance2)

#m2_allscales <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban +State+ KahanS + KahanH + NPRIDENUCLEAR + PRIDENUCLEAR + DEVNUCLEAR + PROSPERNUCLEAR, data = fascale_scores)
# Print model summary
#summary(nuclearacceptlm)

ggplot(acceptance2, aes(x = Pdevelop, y = Nuclear)) +
  geom_point() +  # or geom_line() depending on how you want to visualize it
  facet_wrap(~ State) +  # This will create separate plots for each State
  labs(title = "Net benefit Nuclear vs Pdevelop by State",
       x = "Pdevelop",
       y = "net ben Nuclear") +
  theme_minimal()

@@

sfascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Solar","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR", "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  na.omit()

@@

# SOLAR : CFA on kahan scale and eco-pol scale

# kahan scores for solar 
sfascales <- codedmodule2 %>%
    filter(
    rowSums(is.na(dplyr::select(., starts_with("K_")))) == 0 &  # This line ensures that rows with any NA in columns starting with         "K_" are   filtered out.
    !is.na(WEALTHLIM) & 
    !is.na(MECHANISATION) & 
    !is.na(DECISIONDECEN) & 
    !is.na(DECISIONCEN) & 
    !is.na(INDUSTRYLARGE) & 
    !is.na(INDUSTRYSMALL) & 
    !is.na(ECONOMYGLOBAL) & 
    !is.na(ECONOMYLOCAL) & 
    !is.na(ENVOVERDEV) & 
    !is.na(DEVOVERENV) & 
    !is.na(OWNERPVT) & 
    !is.na(OWNERNOREG) & 
    !is.na(OWNERPUB) & 
    !is.na(OWNERREG) & 
    !is.na(DISPLACESOLAR) & 
    !is.na(POLLUTESOLAR) & 
    !is.na(HEALTHSOLAR) & 
    !is.na(JOBSSOLAR) & 
    !is.na(BEAUTYSOLAR) & 
    !is.na(PRIDESOLAR) & 
    !is.na(NPRIDESOLAR) & 
    !is.na(DEVSOLAR) & 
    !is.na(PROSPERSOLAR) & 
    !is.na(RELYSOLAR)
  )

  #dplyr::select(starts_with(c("K_","Risky_Solar","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%na.omit()

sKahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA
sKahan_cfa <- cfa(sKahan_fas, data = sfascales, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
#summary(sKahan_cfa, fit.measure= TRUE, standardized = TRUE)

sKahan_scores <- predict(sKahan_cfa, newdata = sfascales)

sKahan_Kscores <- cbind(sfascales, sKahan_scores)

sm1_kahan <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = sKahan_Kscores)

## CFA on ecopol vars for solar energy

secopol_fas <- '
  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR + INDUSTRYSMALL + OWNERREG + MECHANISATION
  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR
'

secopol_cfa <- cfa(secopol_fas, data = sfascales, std.lv = TRUE)
summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)

# Cronbach's alpha test on Pdevelop and Ndevelop for Solar energy

solarpdevelop <- sfascales %>%
  dplyr::select(HEALTHSOLAR, BEAUTYSOLAR, DISPLACESOLAR, POLLUTESOLAR, INDUSTRYSMALL, OWNERREG, MECHANISATION)%>%
  na.omit()

solarpdevelop.alpha <- psych::alpha(solarpdevelop, check.keys = TRUE)

# alpha is strong at c!

solarndevelop <- sfascales %>%
  dplyr::select(DEVSOLAR, PRIDESOLAR, NPRIDESOLAR, PROSPERSOLAR)%>%
  na.omit()

solarndevelop.alpha <- psych::alpha(solarndevelop, check.keys = TRUE)

#alpha is strong at 0.86!

## Solar Energy : CFA on Combined Scale (2 Factor Solution)

Solar People Centered Development alpha = 0.75

Solar Nationalist Development alpha = 0.86

# Extract parameter estimates
sparams <- parameterEstimates(secopol_cfa, standardized = TRUE)%>%
   slice(1:(n()-15))

sparams1 <- sparams %>%
  mutate(rhs = case_when(
  rhs == "DISPLACESOLAR" ~ "Solar energy is leading to displacement of people from their land",
  rhs == "BEAUTYSOLAR" ~ "Solar energy spoils the natural beauty of the landscape",
  rhs == "POLLUTESOLAR" ~ "Solar energy increases pollution of air/water/land",
  rhs == "HEALTHSOLAR" ~ "Solar energy poses a great risk to the health of people living around it",
  rhs == "JOBSSOLAR" ~ "Solar energy will bring jobs to the local community",
  rhs == "PRIDESOLAR" ~ "I would be proud if my community used Solar energy",
  rhs == "NPRIDESOLAR" ~ "Solar energy is a mark of pride for our nation",
  rhs == "DEVSOLAR" ~ "Solar energy pushes forward the country's development",
  rhs == "PROSPERSOLAR" ~ "Solar energy brings economic prosperity to the surrounding regions",
  rhs == "RELYSOLAR" ~ "I don't like the idea that I have to rely on the government for electricity from Solar energy",
  rhs == "INDUSTRYSMALL" ~ "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  rhs == "OWNERREG" ~ "Regardless of ownership, the government should pass strong regulations and implement them",
  rhs == "MECHANISATION" ~ "Rapid mechanization of work is taking away jobs from workers in this country",
